### 2014-01-11 docs/reports/finalreport/development.tex
adding new screen-shot

\subsection{Order}
Order system is a full client-side web-page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS. By applying MVVM model, the data submitted in each step is stored in View-Model and used in the next steps. The system screen-shots of ordering process are shown in Figure\ref{fig:order-1}, Figure\ref{fig:order-2} and Figure\ref{fig:order-3}.  The payment process shown in Figure\ref{fig:order-3} is verified by a third-party service which supports different payment cards.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
\caption{Order - entering primitive data
\label{fig:order-1}}
\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
\caption{Order - selecting translator
\label{fig:order-2}}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
\caption{Order - payment process
\label{fig:order-3}}
\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
\caption{Data Accumulating - selecting translator
\label{fig:dataaccumulating}}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[scale=\figurescaling]{figures/chat.jpg}
\caption{Scheduling
\label{fig:scheduling}}
\includegraphics[scale=\figurescaling]{figures/chat.jpg}
\caption{Chat system
\label{fig:chat}}
\end{center}
\end{figure}

>>>>

\subsection{Order}
Order system is a full client-side web-page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS. By applying MVVM model, the data submitted in each step is stored in View-Model and used in the next steps. The system screen-shots of ordering process are shown in Figure\ref{fig:order-1} and Figure\ref{fig:order-2}.  The payment process is verified by a third-party service which supports different payment cards.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
\caption{Order - entering primitive data
\label{fig:order-1}}
\includegraphics[scale=\figurescaling]{figures/order-2.jpg}
\caption{Order - selecting translator
\label{fig:order-2}}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[scale=\figurescaling]{figures/dataaccumulation.jpg}
\caption{Data Accumulating - selecting translator
\label{fig:dataaccumulating}}
\includegraphics[scale=\figurescaling]{figures/chat.jpg}
\caption{Chat system
\label{fig:chat}}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[scale=\figurescaling]{figures/scheduling.jpg}
\caption{Scheduling
\label{fig:scheduling}}
\end{center}
\end{figure}

### 2014-01-11 docs/reports/finalreport/introduction.tex
adding new screen-shot

\section{Introduction}
As a hub for professional translation services, nativy \cite{nativy}(founded 2011 in Vienna) offers its customers top-quality translations at reasonable terms.

The company works exclusively with qualified translators into their native language. All nativy translations are reviewed in accordance with EN $15038$, the European Quality Standard for Translation Services, and translators have to provide evidence of the required qualifications stipulated in the standard by means of their résumé.

>>>>

\section{Introduction}
As a hub for professional translation services, the platform offers its customers top-quality translations at reasonable terms. All translations are reviewed and have to provide evidence of the required qualifications stipulated in the standard by means of their résumé.
